Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-17 paper_jasa.tex
figure 10

\begin{figure*}[hbtp]
   \centering
       \includegraphics[width=0.95\textwidth]{p_val_log_counts.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the sixty (60) individual lineups for experiment 1. \blue{Red indicates the} plot with the lowest $p$-value, and \blue{blue indicates the} actual data plot, when it is different from that with the lowest $p$-value. Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. Empty cells indicate no lineup for that combination of parameters. Highest counts tend to be the plot in the lineup having the lowest $p$-value.}
       \label{fig:P-val_log}
\end{figure*}

>>>>

\begin{figure*}[hbtp]
   \centering
      \includegraphics[width=0.95\textwidth]{p_val_log_counts-a.pdf}
       \includegraphics[width=0.95\textwidth]{p_val_log_counts-b.pdf}
  %      \includegraphics[width=0.95\textwidth]{p_val_log_counts.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the sixty (60) individual lineups for experiment 1. %\blue{Red indicates the} plot with the lowest $p$-value, and 
       \blue{blue indicates the} actual data plot, when it is different from that with the lowest $p$-value. The columns of both top and bottom panel are ordered according to effect size, rows within panels show replicates for each parameter combination.
       %Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. Empty cells indicate no lineup for that combination of parameters. Highest counts tend to be the plot in the lineup having the lowest $p$-value.
       }
       \label{fig:P-val_log}
\end{figure*}
